---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
suppressPackageStartupMessages({
  library(ggplot2)
})

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.height = 2
)
```

# ggreverse

<!-- badges: start -->
![](https://img.shields.io/badge/Status-alpha-orange.svg)
![](https://img.shields.io/badge/Version-0.1.0-blue.svg)
<!-- badges: end -->

`ggreverse` takes a ggplot object and returns the code to create that plot.

This package was written as a learning exercise to help me figure out 
some of the internal structure of a ggplot object.



## ToDo

* Reverse engineering of facetting and scales from a plot object.
* `aes_string()` is currently unsupported.
* Using tidyeval in `aes()` calls is currently unsupported.
* Lots of other stuff :)

## Installation

You can install from [GitHub](https://github.com/coolbutuseless/) with:

``` r
# install.packages("remotes")
remotes::install_github("coolbutuseless/ggreverse")
```



## Example `ggreverse::convert_to_code()`

1. Create a ggplot
2. Convert the ggplot back into code using `ggreverse`
3. Convert the code back into a plot

```{r}
library(ggreverse)

plot_df <- mtcars

# Create a ggplot2 plot object
p <- ggplot(plot_df) +
  geom_point(aes(mpg, wt), size = 3) +
  labs(title = "hello") +
  theme_bw() + 
  coord_equal()
```

```{r echo = FALSE}
p
```


```{r echo=TRUE, eval=FALSE}
# Convert the plot object back into code
plot_code <- ggreverse::convert_to_code(p)
plot_code
```


```{r echo=FALSE, eval=TRUE}
plot_code <- convert_to_code(p)
styler::style_text(
  gsub("[+]", "+\n", plot_code)
)
```


```{r}
# Parse the plot code back into a plot - which should match the original plot
eval(parse(text = plot_code))
```


## SessionInfo

Developed against:

* R 3.5.3
* ggplot2 v3.1.1

